Introduction to linear regression

### 2018-11-17 DATA606/Lab7/michael-simple_regression.Rmd
Lab 7 Complete

6.  Is there any apparent pattern in the residuals plot? What does this indicate
    about the linearity of the relationship between runs and at-bats?

@@

7.  Based on the histogram and the normal probability plot, does the nearly 
    normal residuals condition appear to be met?

@@

8.  Based on the plot in (1), does the constant variability condition appear to 
    be met?

@@

@@

@@

@@

@@

>>>>

6.  Is there any apparent pattern in the residuals plot? What does this indicate
    about the linearity of the relationship between runs and at-bats? **No there is no apparent pattern in the residuals.**

@@

7.  Based on the histogram and the normal probability plot, does the nearly 
    normal residuals condition appear to be met?  **Yes it appears to be normal**

@@

8.  Based on the plot in (1), does the constant variability condition appear to 
    be met? **Yes it does.**

@@

    **I think homeruns would be a good predictor because it gets to the skill of the player.  new_obs would probably be better but it is not a traditional variable. **

    ```{r}
    plot(mlb11$homeruns, mlb11$runs)
    ```

    **Yes this appears to be a positive linear relationship.**

@@

    ```{r}
    m3 <- lm(runs ~ homeruns, data = mlb11)
    summary(m3)
    ```
    **The $R^2$ for this model is `r summary(m3)$r.squared` which is higher than `r summary(m1)$r.squared`.  It does a better job of predicting.  You can tell because the $R^2$ is higher and the residual standard error is lower.**

@@

    ```{r}
    highest_r_squared <- 0
    # Loop through all the traditional variables
    for(v in c('at_bats', 'hits', 'homeruns', 'bat_avg', 'strikeouts', 'stolen_bases', 'wins')){
      temp <- mlb11[,c('runs', v)]
      model <- lm(runs ~ ., data = temp)
      r_squared <- summary(model)$r.squared
      if(r_squared > highest_r_squared){
        best_var <- v
        highest_r_squared <- r_squared
        best <- temp
        best_model <- model
      }
    }

    plot(best)
    summary(best_model)
    ```

@@

    ```{r}
    # Loop through all the Moneyball variables
    best_r_squared <- summary(best_model)$r.squared
    for(v in c('new_onbase', 'new_slug', 'new_obs')){
      temp <- mlb11[,c('runs', v)]
      model <- lm(runs ~ ., data = temp)
      r_squared <- summary(model)$r.squared
      if(r_squared > best_r_squared){
        message(paste(v, "outpreforms", best_var, "(", round(r_squared, 2), " > ", round(best_r_squared, 2), ")"))
        best_model <- model
        best_data <- temp
      }
    }
    ```

@@

    **Linearity : No pattern to the residuals.**

    **Constant variability : Yes Sir!**

    ```{r}
    plot(best_model$residuals ~ mlb11$new_obs)
    abline(h = 0, lty = 3)
    ```

    **Nearly normal residuals : Check**
    ```{r}
    qqnorm(best_model$residuals)
    qqline(best_model$residuals)
    ```
